\documentclass[format=draft,language=chinese,degree=phd,table,usenames,dvipsnames]{hustthesis}

\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{algorithm2e, setspace}
% \usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{etoolbox}

\newcommand{\algostretch}{1.25}
%\onehalfspacing
\setstretch{1.66666}
%\setlength{\tabcolsep}{1.2}
\renewcommand{\arraystretch}{1.2}

\newcommand{\red}[1]{{\color{red}{#1}}}
\def\fp{\textit{fp}}
\def\ft{\textit{ft}}
\def\vfp{\textit{vfp}}
\def\vft{\textit{vft}}
\def\mr{\textit{mr}}
\def\vmr{\textit{vmr}}
\def\sz{\textit{sz}}
\def\bw{\textit{bw}}
\def\trfc{\textit{trfc}}
\def\fr{\textit{fr}}
\def\dram{\textit{dram}}
\def\pcm{\textit{pcm}}
\def\miss{\textit{miss}}
\def\wss{\textit{wss}}

%\def\FC{\textit{FractionCache}}
\def\FC{\text{FractionCache}}

\def\AR{\textit{AR}}
\def\MR{\textit{MR}}
\def\SFMR{\textit{SFMR}}

\stuno{D201177565}
\schoolcode{10487}
\title{面向群智感知的\\边缘计算资源调度机制研究}{Resources Scheduling Mechanisms in Edge Computing for Mobile Crowdsensing}
\author{侯海翔}{Haixiang Hou}
\major{计算机系统结构}{Computer Architecture}
\supervisor{金海\hspace{1em}教授}{Prof. Hai Jin}
\date{2019}{5}{26}

\zhabstract{
% 论文针对移动群智感知中感知、通信、计算三个重要环节


移动群智感知利用众包的方式将数据采集任务分发给无处不在的智能移动设备，通过设备内集成的各种传感器收集感知数据。
% 相较于传统的无线传感网络，移动群智感知的执行效率更高、适用范围更广、部署成本更低。
% 早期阶段，移动群智感知常借助云计算技术处理大量的感知数据。
% 如今，万物互联的时代已经来临，成倍增加的移动设备，不仅扩大了移动群智感知的覆盖范围，也让感知数据的体积上升到更大的数量级。
边缘计算作为与云计算模型互补的分布式计算模型，其覆盖范围广、涵盖设备多、可耦合多种异构网络，这些特性为移动群智感知底层支撑提供了新的契机。
另一方面，移动设备利用端到端（Device-to-Device，简称D2D）通信，在感知过程中实现了成本更低的数据交互。
如何结合边缘计算和 D2D 通信实现『大范围、低延时』的感知应用，已成为目前亟待解决的重要课题。

% 移动群智感知应用包含三个重要过程：感知、通信和数据处理。
% 尽管边缘计算的分布式特性和移动群智感知相吻合，但是随着移动设备的增加、感知数据的膨胀，这三个过程都面临着不同的资源调度问题。
% 在感知过程中，由于移动设备并不具备感知任务的发现能力，感知任务的发起者通常借助边缘服务器、端到端通信等手段进行感知任务的分发工作。
% 而为了保障感知质量，需要利用大量的移动设备收集足够的感知数据。
% 因此，如何利用现有资源将感知任务快速部署到目标区域内尽可能多的移动设备上，是感知过程的重要工作之一。
% 在通信过程中，收集到的感知数据需要经过网络传输进行汇总，然后交付给计算服务器进行数据处理、数据分析和数据挖掘。
% 出于能耗、成本、以及主干网络资源占用等因素，感知数据的上传已经多采用端到端通信为主、蜂窝通信为辅的指导思想。
% 因此，在边缘网络中存在不同的异构网络资源。
% 面对海量的感知数据传输，如何划分网络资源、分配数据链路，是降低通信成本、节省网络资源的重要研究工作。
% 在数据处理过程中，移动群智感知通常采用云端融合的思想，将数据预处理工作委托给边缘服务器，以达到加速最终数据处理的目的。
% 同时，边缘服务器也可以作为数据收集的代理节点，避免感知数据直接上传云端造成的主干网络资源占用。
% 面对智能城市感知等大范围群智感知应用，如何针对感知任务的需求部署边缘服务器、调度数据预处理任务，也是提高感知质量的一项重要研究工作。
% 围绕移动群智感知应用的三个重要过程，提出了多个针对性的资源调度优化机制对感知质量进行优化。

% 移动群智感知应用包含三个重要过程：感知、通信和数据处理。
% 在感知任务执行过程中，移动设备的运动状态会






移动群智感知应用包含三个重要过程：感知、通信和数据处理。
在感知过程中，%由于移动设备并不具备感知任务的发现能力，
通常借助边缘服务器、端到端（Device-to-Device，简称 D2D）通信等手段加快感知任务的分发和感知数据的收集。
如何借助多边缘服务器和 D2D 通信提高感知任务的执行效率、扩大感知服务的覆盖范围，是提高感知质量的重要工作之一。
在通信过程中，为了减少通信成本开销和主干网资源占用，移动群智感知中的数据交互多采用 D2D 通信为主、蜂窝通信为辅。 
面对海量的感知数据传输，如何借助软件定义网络技术（Software-Defined Networking，简称SDN）合理调度网络资源、规划传输路径，也是提高感知任务执行效率、减少执行成本的关键研究工作。
在数据处理过程中，移动群智感知多采用云端融合的思想，借助边缘服务处理海量的感知数据。
% 将数据处理工作委托给边缘服务器，以达到加速最终数据处理的目的。
面对智慧城市感知等大范围群智感知应用，如何针对感知任务的需求部署边缘服务器、调度数据处理服务，也是提高感知质量的一项重要研究工作。
围绕移动群智感知应用的三个过程中面临的主要问题，提出了多个针对性的资源调度优化机制对感知质量进行优化。

针对感知过程
%中移动设备的运动状态对D2D通信造成的影响
，提出了基于感知质量的任务调度机制，以提高感知任务在多任务传播源、多数据接收源场景下的执行效率。
% 由于D2D通信的引入，感知任务的部署和移动设备的运动状态密切相关。
目前的分析方法，无法准确描述移动群智感知应用的完整执行过程。
基于此现状，利用随机过程分析将感知执行过程转化为数学语言，并使用常微分方程组定义了感知任务的执行过程。
借助数学分析，该机制找出了移动设备在机会式通信网络中影响感知任务传播速度和感知数据收集速度的主要因素。
通过二阶段决策算法，制定感知任务的分发策略和感知任务执行时间划分方法，在感知任务生命周期内提高感知质量。

针对通信过程，提出了基于计算任务卸载的网络资源调度机制，利用SDN优化边缘网络中移动设备的通信效率。
在移动群智感知应用中，%移动设备的数据处理能力、网络通信能力存在个体差异。
对于能力有限的移动设备，可以将原始感知数据直接交给边缘服务器处理。
然而，诸如视频、图像类的原始感知数据体积较大，容易导致边缘网络中的通信资源失衡，甚至引起网络堵塞。
基于此现状，利用排队论，建立了计算卸载决策、能耗以及链路资源之间的整数线性规划模型。
通过对该模型的学习和分析，在保障计算任务卸载收益最大化的同时，实现了边缘网络中的链路负载均衡。

针对数据处理过程，提出了基于城市社会网络的边缘服务调度机制，解决在城市范围内实施移动群智感知时边缘服务的部署的调度问题。
为了获取城市主体和物理对象的数字信息，智慧城市研究主要借助移动群智感知来收集基础数据。
% 利用人类生活中无处不在的移动设备，移动群智感知可以提取城市主体和物理对象的大量数字信息，作为智慧城市研究的基础数据。
在该应用场景下，通常会借助城市居民的社交网络特征来部署边缘服务，提高移动群智感知的服务质量。
基于此现状，该机制借助城市中已有的公交网络和公共交通中的乘客流动特征，建立了乘客轨迹、公交路线和边缘服务部署决策的混合整数线性规划模型。
通过对该模型的分析求解，降低了城市感知应用中的边缘服务部署成本。

综上所述，围绕移动群智感知的三个主要过程，利用边缘计算资源调度优化机制可以减少数据传输、数据处理的时间，在保障感知质量的前提下合理降低能耗成本和服务成本。
同时，与D2D通信的深度结合，也让移动群智感知为 5G 时代的到来，打下坚实的基础。


% 感知任务的发起者通常借助任务分发服务将感知任务部署到相应的移动设备上。
% 因此，感知任务在分发时，会使用边缘服务器和端到端通信，来扩大感知任务的覆盖范围并加快任务分发的速率。
% 将任务分发服务部署在边缘服务器，能够在移动设备的近端分发感知任务。
% 但是移动设备之间的网络结构差异、地理分布差异、以及运动状态变化等异构环境，让感知任务的分发速率不具备可控性，空间覆盖也无法得到准确的保障。
% 这将导致局部数据缺失、冗余数据过多，最终影响感知质量。





}

\zhkeywords{边缘计算，移动群智感知，端到端通信}

\enabstract{
Abstract
Mobile crowdsensing distributes sensing tasks to ubiquitous mobile devices by crowd, through collecting sensing data from various integrated sensors inside of devices. Edge computing, as a complementary distributed computing model to cloud computing model, provides new opportunities for mobile crowdsensing underlying support, due to its wide coverage, abundant devices, and heterogeneous networks. On the other hand, mobile devices utilize D2D (Device-to-Device) communication to reduce the cost of data interaction in the sensing process. Therefore, how to combine edge computing and D2D communication to achieve wide coverage and low latency mobile crowdsensing is remained to be solved. 

Mobile crowd sensing application contains three crucial processes: sensing, communication, and data processing. In the sensing process, mobile crowdsensing task initiator generally employ edge servers, D2D communication and so on to accomplish sensing task dissemination and sensing data collection. One of the most important works of enhancing the quality of sensing is figuring out how to use edge servers and D2D communication to improve the efficiency of sensing task and enlarge the sensing coverage. And in the communication process, data interaction in mobile crowd sensing mainly adopts D2D communication supplemented by cellular communication, in order to decrease the communication overhead and the occupation of backbone network resource. Faced with massive amounts of sensing data transmission, it’s also an important research to work out how to use SDN (Software-Defined Networking) reasonable schedule network resource and plan transmission path to improve the efficiency of sensing task and reduce the cost. In the data processing process, edge computing model is widely used in mobile crowd sensing, processing massive sensing data by edge servers. We propose several resource schedule and optimization technologies to enhance the quality of sensing, and to solve problems above individually. 

First, in the sensing process, we propose tasks schedule technology based on quality of sensing, to enhance the efficiency of sensing tasks in multiple source and receivers. However, the existing analytical methods couldn’t describe the complete execution process of mobile crowdsensing precisely. Thus we convert the sensing process into mathematics using stochastic analysis, and define the sensing process using ODEs (Ordinary Differential Equations). This technology finds out the major factors of influence sensing tasks propagate speed and sensing data collect speed in mobile devices in D2D communication networks through math analysis. 

Second, in the communication process, we propose a network resource scheduling mechanism based on task offloading, and use SDN to optimize the communication efficiency of mobile devices in edge networks. For mobile devices with limited capabilities, the original sensing data can be directly handed over to the edge server for processing. However, the volume of raw sensing data, such as video and image, is huge, which easily leads the network congestion. Based on this situation, we build an integer linear programming model ( ILP ) between offload decision, energy consumption, and network resource which is established. Through the study and analysis of the model, we archieve the load balance of links in the edge network and maximize the benefits of computing task offloading.

Third, in the data processing, we proposes an edge service scheduling mechanism based on the urban social network to solve the deployment problem of edge service  for mobile crowdsensing in cities. Under this scenario, edge services are usually deployed with the help of the social network characteristics of urban residents to improve the sensing quality of mobile crowdsensing. Based on this situation, the mechanism builds a mixed integer linear programming model ( MILP ) with passenger trajectory, bus lines, and edge service deployment decisions by using the existing bus network and passenger flow characteristics in public transportation. Through the analysis of this model, the deployment cost of edge services in urban mobile crowdsensing applications is reduced.

In summary, focus on the three main processes of mobile crowdsensing, we use edge resource scheduling optimization technologies to reduce the time of data transmission and data processing, and reasonably reduce the energy consumption and service cost, and ensuring the sensing quality. At the same time, the deep combination with D2D communication also makes mobile crowdsensing more suitable for IoT scenarios.
}
\enkeywords{Edge computing, Mobile crowdsensing, D2D Communication}

\begin{document}

\frontmatter
\maketitle
\makeabstract
\tableofcontents
% \listoffigures
% \listoftables
\mainmatter
\input{Macro_Define}

\input{Chapter-Introduction}

\input{Chapter-UIC}

\input{Chapter-ISPA}

\input{Chapter-MONET}

\input{summary}


\begin{ack}


\end{ack}

\bibliography{ref}

\appendix


\begin{publications}
\item Liao X, Li H, Jin H, \textbf{Hou H}, Jiang Y, Liu H. VMStore: Distributed storage system for multiple virtual machines. SCIENCE CHINA Information Sciences, 2011, 54(6):1104-1118. DOI 10.1007/s11432-011-4273-0
\item \textbf{Hou H}, Jin H, Liao X, Zeng D. Multi-path Routing for Energy Efﬁcient Mobile Ofﬂoading in Software Deﬁned Networks. in Proceedings of The IEEE International Symposium on Parallel and Distributed Processing with Applications, 2017, pp. 360-367. DOI 10.1109/ISPA/IUCC.2017.00058
\item \textbf{Hou H}, Jin H, Liao X, Zeng D. Stochastic Analysis on Fog Computing Empowered Mobile Crowdsensing with D2D Communications. in Proceedings of The IEEE International Conference on Ubiquitous Intelligence and Computing, 2018, pp. 656-663. DOI 10.1109/SmartWorld.2018.00131
\item \textbf{Hou H}, Jin H, Liao X, Zeng D. Cost Efficient Edge Service Placement for Crowdsensing via Bus Passengers.
\end{publications}

\end{document}

\endinput
%%
%% End of file `hustthesis-zh-example。tex'。
